factor_explorer

### 2014-06-20 ijlyttle/factor_explorer.Rmd
adds comments on packages

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)
library(shiny)
```

>>>>

```{r load_libraries, message=FALSE}
library(stringr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)
library(shiny)

# 2014-06-20
# for what it's worth, I'm running the latest versions of RStudio (0.98.932 )and 
# github versions of "rstudio/shiny", "rstudio/rmarkdown", "yihui/knitr"
```
